---
title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Last sentence."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
```

# Introduction
First paragraph

Second paragraph 

Third paragraph


This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

# Data
```{r, include=FALSE, echo=FALSE}
# Read the reduced and cleaned data, modification done in data-preparation.r file
reduced_data1 <- read_csv("outputs/data/prepared_gss1.csv")
reduced_data2 <- read_csv("outputs/data/prepared_gss2.csv")
c_data <- read_csv("outputs/data/combined_data.csv")
```

Data Explanation 

```{r fig1,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
    facet_grid(~year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on arms"}
c_data$natarms <- factor(c_data$natarms,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natarms)  %>%
   ggplot(aes(x= natarms,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig3,echo=FALSE,fig.cap = "Distribution of national spending on childcare"}
c_data$natchld <- factor(c_data$natchld,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natchld)  %>%
   ggplot(aes(x= natchld,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r}

```

\newpage

# Results



# Discussion


## Summary




## Weaknesses and how we should proceed in the future



\newpage

\appendix

# Appendix {-}



## End Page

Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
sangwoong.lee@maill.utoronto.ca and young.suk@mail.utoronto.ca

\newpage


# References
Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
