---
title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "COVID-19 influences on U.S citizens' mind regarding government actions"
author: 
  - SangWoong Lee
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Last sentence."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
library(modelsummary)
```

# Introduction
Although we are currently heading back to life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style especially until end of 2021. For instance, remote work or wearing masks in public spaces has become usual. Of course, many of us feel uncomfortable about the strict sanctions. Then, my question was who should be in charge of this pandemic. Speaking of results, it should be all of us. Probably, without radical advances in technology, such virus would not exist. However, blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions. Then, which fields  are more vulnerable to criticism? This brings me to write this paper. 

This paper is going to explore changes in U.S citizen opinions on government spending levels before and after COVID-19. Following that, I have obtained U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables changed during the pandemic. Since I aimed to figure out government spending on various fields, I mainly extracted national spending levels as the variables. However, there remains a clear gap that needs to be filled. Because this paper is about general thoughts changes on government spending levels, it was hard to make decisions that some changes were due to the pandemic or not. For instance, 26% of participants said national spending on arms was too much in 2018, and 32% of them said it was too much in 2021. It is hard to tell whether the increase is solely due to the pandemic or not. 

In order to discern the changes by the pandemic, I was required to research U.S society backgrounds in 2018 and 2021, and they were used to along with data analysis. By plotting graphs for comparison, I sorted responses as three factors: Positive, Negative and unchanged. For instance, for positive response, many of participants required more national budgets on welfare. 
In general, national spending on public service such as education earned positive. On the other hand, national spending on arms, or foreign aids earned negative. Of course, there exists exceptions, and they are going to be dealt with in result and discussion session. 

This paper is important in a sense that it can present new plans and visions for government budgets. Also, in a broader sense, other countries can refer to this paper for simple comparison. 
Before we jump into the main session, I am going to briefly introduce you remained index of this paper, and what they are about.

2) Data: you are going to see how data was collected and sorted

3) Model: you are going to observe which variables belong to negative, positive and unchanged.

4) Results: you are going to read summary and analysis of data. 

5) Discussion: what is remained to be solved. 

6) Appendix and References.

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

# Data
```{r, include=FALSE, echo=FALSE}
# Read the reduced and cleaned data, modification done in data-preparation.r file
c_data <- read_csv("outputs/combined_data.csv")
```

For this paper, I aimed to find out changes in U.S citizens' minds regarding the government before and after COVID-19 outbreak. Following that, I obtained datasets from U.S GSS 2018 and 2021 considering first outbreak of COVID-19, which was in Dec 2019. There are numerous surveys about COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS. Most COVID-19 surveys were specifically aimed for healthcare fields. For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys. On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes than specific areas.
Among countless variables existing in U.S GSS, I chose national spending levels and government actions. Since I needed to use two different years for comparison, I had to extract variables that were in common, then combined them. Also, since number of samples was different, converting sample size to percentage was needed. 

The variables I collected were as followed:

1) National spending on various fields (foreign aids, arms, children, big cities, crime, drug,
education, new energy, environment, fare, healthcare, mass transportation, parks, race, roads, science and social security )

2) Government's actions (income equality, the sick, the poor)

3) Respondents' health

There exists 17 variables in national spending and 3 variables regarding government actions. Since, dealing with all variables in this session would take much spaces, for those that did not change much from 2018 to 2022, I am going to deal with in Appendix. 

First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns and noticeable changes between two graphs 2018 and 2021. For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes. On the other hand, although figure \@ref(fig:fig6) presents the same pattern, changes in percentage are relatively fluctuating than others. For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021. Therefore, with respect to the two aspects, I am going to explain my data here.

1) National spending (Foreign aid, Arms, Drug addicts, Welfare, race)

- Foreign Aid

Let's take a look at figure \@ref(fig:fig1). In general, majority of respondents answered either "Too much" or "About right". What is interesting here is 7.8% decrease in "Too little" and 9.2% increase in "Too much". These numbers might seem subtle, however if we put this into whole population of U.S, it is 25.7 million and 30.34 million respectively. 

- Arms

If you take a look at figure \@ref(fig:fig2), you can observe two different patterns. "Too little" and "Too much" in 2018 has been reversed in 2021. If you think about U.S withdraw from Afghanistan in 2021, this would make sense.

- Drug Addicts

This is an indicator that contradicts with drug overdose death data. According to CDC, death rate from drug overdoes is increasing over years. However, figure \@ref(fig:fig6) presents the decreasing in "Too little", although it is  the highest among three indicators. 

- Welfare

Welfare graph seems relatively obvious than those above. Figure \@ref(fig:fig10) shows us that more voices on increasing national spending on welfare. Here I strongly suspect the COVID-19 outbreak as a main reason for the change. 

- Race

Figure \@ref(fig:fig14) shows the national spending on improvement in Black conditions. Even though "Too little" is higher than others, it decreased over the years. On the other hand, "Too much" increased by 9.4%. As I mentioned above, this percent is huge. Unfortunately, there is a limit in this variable. Black alone cannot represent all races in U.S, thus it is hard to generalize all races from this data. However, the differences observed in this graph possesses valuable meanings. 

2) Government actions

- Income equality and help poor

This two variables are very similar. Income equality is regarding whether government should impose more taxes on the rich for better income equality or not, and help poor is whether government should be responsible for helping the poor or not. Thankfully, they both present similar pattern, which enhances the reliability about the survey. Majority thinks that government and individuals both are responsible for income differences. One thing to notice here is that voice for government responsibility increased over years.

- The sick

The two graph in figure \@ref(fig:fig19) seems very similar, but this does not mean that it does not possess valuable meanings. In 2020 - 2021 when U.S GSS 2021 was conducted, although COVID-19 cases did not surge up as much as 2022, but with eyes in 2021, it was increasing. However, before and after COVID-19, there is no difference in response regarding government actions toward the sick. Majority think that more actions needed toward the sick from the government

3) Respondents' health

Most of participants were in good health conditions in figure \@ref(fig:fig18). One thing to notice here is that participants health conditions increased. 

```{r fig1,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
           "National Spending on Foreign Aid") +
    facet_grid(~year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on arms"}
c_data$natarms <- factor(c_data$natarms,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natarms)  %>%
   ggplot(aes(x= natarms,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
           "National Spending on Arms") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig3,echo=FALSE,fig.cap = "Distribution of national spending on childcare"}
c_data$natchld <- factor(c_data$natchld,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natchld)  %>%
   ggplot(aes(x= natchld,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
           "National Spending on Childcare") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig4,echo=FALSE,fig.cap = "Distribution of national spending on big cities problems"}
c_data$natcity <- factor(c_data$natcity,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natcity)  %>%
   ggplot(aes(x= natcity,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
           "National Spending on Big Cities Problems") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig5,echo=FALSE,fig.cap = "Distribution of national spending on halting crime rates"}
c_data$natcrime <- factor(c_data$natcrime,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natcrime)  %>%
   ggplot(aes(x= natcrime,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
           "National Spending on Halting Crime Rates") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig6,echo=FALSE,fig.cap = "Distribution of national spending on dealing with drug addicts"}
c_data$natdrug <- factor(c_data$natdrug,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natdrug)  %>%
   ggplot(aes(x= natdrug,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Dealing with Drug Addicts") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig7,echo=FALSE,fig.cap = "Distribution of national spending on improving education"}
c_data$nateduc <- factor(c_data$nateduc,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nateduc)  %>%
   ggplot(aes(x= nateduc,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Improving Education") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig8,echo=FALSE,fig.cap = "Distribution of national spending on developing alternatives energy sources"}
c_data$natenrgy <- factor(c_data$natenrgy,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natenrgy)  %>%
   ggplot(aes(x= natenrgy,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Developing Alternatives Energy") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig9,echo=FALSE,fig.cap = "Distribution of national spending on protecting environment"}
c_data$natenvir <- factor(c_data$natenvir,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natenvir)  %>%
   ggplot(aes(x= natenvir,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Protecting Environment") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig10,echo=FALSE,fig.cap = "Distribution of national spending on Welfare"}
c_data$natfare <- factor(c_data$natfare,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natfare)  %>%
   ggplot(aes(x= natfare,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Welfare") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig11,echo=FALSE,fig.cap = "Distribution of national spending on improving health"}
c_data$natheal <- factor(c_data$natheal,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natheal)  %>%
   ggplot(aes(x= natheal,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Improving Health") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig12,echo=FALSE,fig.cap = "Distribution of national spending on mass transportation"}
c_data$natmass <- factor(c_data$natmass,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natmass)  %>%
   ggplot(aes(x= natmass,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Mass Transportation") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig13,echo=FALSE,fig.cap = "Distribution of national spending on park and recreation"}
c_data$natpark <- factor(c_data$natpark,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natpark)  %>%
   ggplot(aes(x= natpark,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Park and Recreation") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig14,echo=FALSE,fig.cap = "Distribution of national spending on improving the conditions of black"}
c_data$natrace <- factor(c_data$natrace,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natrace)  %>%
   ggplot(aes(x= natrace,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Improving Conditions of Black") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig15,echo=FALSE,fig.cap = "Distribution of national spending on highway and bridges"}
c_data$natroad <- factor(c_data$natroad,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natroad)  %>%
   ggplot(aes(x= natroad,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Highway and Bridge") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig16,echo=FALSE,fig.cap = "Distribution of national spending on scientific research"}
c_data$natsci <- factor(c_data$natsci,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natsci)  %>%
   ggplot(aes(x= natsci,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Supporting Scientific Research") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig17,echo=FALSE,fig.cap = "Distribution of national spending on social security"}
c_data$natsoc <- factor(c_data$natsoc,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(natsoc)  %>%
   ggplot(aes(x= natsoc,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
           "National Spending on Seocial Security") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig18,echo=FALSE,fig.cap = "Respondents self Health Conditions"}
c_data$health <- factor(c_data$health,                                  
                  levels = c("Poor", "Fair", "Good", "Excellent"))
c_data  %>%
  drop_na(health)  %>%
   ggplot(aes(x= health,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "Health Conditions", title = 
           "Respondents' Health Conditions by Self Assessment") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Poor", "2" = "Fair", "3" = "Good", "4" = "Excellent"),
                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
```

```{r fig19,echo=FALSE,fig.cap = "Government and Individuals on Health"}
c_data$helpsick <- factor(c_data$helpsick,                                  
                  levels = c("No", "Somewhat", "Both", "Yes"))
c_data  %>%
  drop_na(helpsick)  %>%
   ggplot(aes(x= helpsick,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "Response", title = 
           "Should Government Be Responsible for Taking Care of Individuals?") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "No", "2" = "Somewhat", "3" = "Both", "4" = "Yes"),
                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
```

```{r fig20,echo=FALSE,fig.cap = "Government and Individuals on Poor"}
c_data$helppoor <- factor(c_data$helppoor,                                  
                  levels = c("No", "Somewhat", "Both", "Yes"))
c_data  %>%
  drop_na(helppoor)  %>%
   ggplot(aes(x= helppoor,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "Response", title = 
           "Should Government Be Responsible for Improving Standard Livings?") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "No", "2" = "Somewhat", "3" = "Both", "4" = "Yes"),
                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))

```

```{r fig21,echo=FALSE,fig.cap = "Government Reducing Income Differences"}
c_data$eqwlth <- factor(c_data$eqwlth)                                 
                  
c_data  %>%
  drop_na(eqwlth)  %>%
   ggplot(aes(x= eqwlth,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4, size = 3) +
    labs(x = element_blank(),y = "Percent", fill = "Levels", title = 
           "Should Government Be Responsible for Reducing Income Differences") +
    facet_grid(~ year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Yes", "7" = "No"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d","#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
```



\newpage

# Results
According to Forbes research, foreign aid spent by U.S is decreasing over years which was 46 billion dollars in 2018 and 38 billion dollars in 2021. In other words, this contradiction means that there could be another factors that possibly influenced thoughts on foreign aids. 


# Discussion


## Summary




## Weaknesses and how we should proceed in the future



\newpage

\appendix

# Appendix {-}
In this session, I am going to deal with remained data explanation. Since no dramatic changes were observed in remained variables, I combined them by patterns. 

1) Decrease in "Too little" and increase in "About right" and "Too much"

- Big cities Problems (figure \@ref(fig:fig4))
- Education (figure \@ref(fig:fig7))


2) Decrease in "Too little" and "About right" and increase in "Too much"

- Childcare (figure \@ref(fig:fig3))
- Crime rates (figure \@ref(fig:fig5))
- New energy (figure \@ref(fig:fig8))
- Social security (figure \@ref(fig:fig17))


3) Decrease in "About right" and increase in "Too little" and "Too much"

- Environment (figure \@ref(fig:fig9))

4) Decrease in "Too much" and increase in "Too little and "About right"

- Road (figure \@ref(fig:fig15))

4) only subtle changes. 

- Mass transportation (figure \@ref(fig:fig12))
- Park and Recreation (figure \@ref(fig:fig13))
- Scientific research (figure \@ref(fig:fig16)) 




## End Page

Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
sangwoong.lee@maill.utoronto.ca and young.suk@mail.utoronto.ca

\newpage


# References
Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.
https://www.forbes.com/sites/adamandrzejewski/2021/08/04/new-report-nearly-300-billion-in-foreign-aid-spent-by-us-government/?sh=6e3454774374
https://www.cdc.gov/drugoverdose/deaths/index.html

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
